I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-25 Paper/introduction.tex
introduction

\item Our third main contribution addresses this practical concern, introducing 
\CMP (Algorithm \ref{algo1}), a pragmatic solution that leverages our theoretical insights. This approach ranks ReLU nodes based on {\color{red} 
the weights of the compensating paths they belong to,
and differentiates their treatment in the MILP model (binary for heavy, linear for light). 
%Notably, Algorithm \ref{algo1} is exceptionally amenable to parallelization, as all nodes within the same layer can be processed simultaneously. Furthermore, 
Our comprehensive empirical evaluation indicates that \CMP provides favorable trade-offs between accuracy and completeness compared to existing methods, 
%lowering the number of 
%undecided inputs from $17.6\%$ ($\beta$-Crown \cite{crown}) to $10.4\%$ 
%on DNN $8 \times 200$ (Table \ref{tab:example}), even 
verifying more than $20\%$ more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN (Table \ref{tab:example3}).}

>>>>

\item Our third main contribution addresses this practical concern, introducing 
\CMP (Algorithm \ref{algo1}), a pragmatic solution that leverages our theoretical insights. This approach ranks ReLU nodes based on {\color{red} 
the weights of the compensating paths they belong to,
and differentiates their treatment in the MILP model (binary for heavy, linear for light). 
%Notably, Algorithm \ref{algo1} is exceptionally amenable to parallelization, as all nodes within the same layer can be processed simultaneously. Furthermore, 
Our comprehensive empirical evaluation indicates that \CMP provides favorable trade-offs between accuracy and completeness compared to existing methods, 
%lowering the number of 
%undecided inputs from $17.6\%$ ($\beta$-Crown \cite{crown}) to $10.4\%$ 
%on DNN $8 \times 200$ (Table \ref{tab:example}), even 
verifying more than $20\%$ more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}) on the larger $6 \times 500$ DNN trained naturally (Table \ref{tab:example3}).}
